### 2021-07-10 docs/manuscript/manuscript.tex
Fix typo in Acknowledgements

\section*{Aknowledgements}
The computational resources (Stevin Supercomputer Infrastructure) and
  services used in this work were provided by the VSC (Flemish Supercomputer
  Center), funded by Ghent University, FWO and the Flemish Government –
  department EWI.

>>>>

\section*{Acknowledgements}
The computational resources (Stevin Supercomputer Infrastructure) and
  services used in this work were provided by the VSC (Flemish Supercomputer
  Center), funded by Ghent University, FWO and the Flemish Government –
  department EWI.
